---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# glouton

<!-- badges: start -->
<!-- badges: end -->

The goal of glouton is to handle browser cookies in shiny. 

It's built on top of [js-cookie](https://github.com/js-cookie/js-cookie).

## Installation

You can install the released version of glouton from [github](https://github.com/ColinFay/glouton) with:

``` r
remotes::install_github("ColinFay/glouton")
```

## Function reference

In the UI, add `use_glouton()` to integrate `{glouton}` to your app.

In the server, you can use: 

+ `add_cookie` to add a session cookie. Takes a name, content, and the `session` object.
+ `fetch_cookies` / `fetch_cookie` to get all or one cookie. Takes the `session` and `input` objects and a name for `fetch_cookie()`
+ `remove_cookie` to remove one cookie. Takes a name of a cookie and the `session` object.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval = FALSE}
library(glouton)
library(shiny)
ui <- function(request){
  tagList(
    use_glouton(),
    textInput("cookie_name", "cookie name"),
    textInput("cookie_content", "cookie content"),
    actionButton("setcookie", "Add cookie"),
    actionButton("getcookie", "get cookie"),
    verbatimTextOutput("cook"),
    verbatimTextOutput("one")
  )
}

server <- function(input, output, session){

  r <- reactiveValues()

  observeEvent( input$setcookie , {
    add_cookie(input$cookie_name, input$cookie_content, session)
  })
  observeEvent( input$getcookie , {
    r$cook <- fetch_cookies(session, input)
  })

  output$cook <- renderPrint({
    r$cook
  })

}

shinyApp(ui, server)
```

## TO DO

+ Support passing domain / path / expire to cookie https://github.com/js-cookie/js-cookie#basic-usage
